Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-08 ms.tex
added last figure to reddening residual discussion

The ony solution we were able to identify that both removed the `bend' vs.
$E(B-V)_{SFD}$ and the temperature dependence of the residual was cutting 
out the ecliptic plane, restricting to $|\beta|>20^{\circ}$ . In this case, we 
completely eliminated the bending behavior of the residual versus 
$E(B-V)_{SFD}$, and significantly reduced the $T_2$ dependence (see Figure
\ref{fig:resid_ecl}), to a peak-to-peak amplitude of only $\sim$10 mmag. We
still included the single-MBB plots (right column), to show that 
the bend versus $E(B-V)_{SFD}$ is eliminated by the $|\beta|$ cut, even
for the single-MBB model. However, the single-MBB residuals still differ
systematically from zero for $T$$\lesssim$$19$ K. Perhaps these improvements in
the two-component reddening residuals after restricting to high ecliptic 
latitude should come as no surprise, given that the ecliptic plane is the most 
obvious systematic problem with the temperature correction upon inspecting the 
full-sky temperature map in Figure \ref{fig:results}.

@@

>>>>

The ony solution we have been able to identify that both removes the `bend' vs.
$E(B-V)_{SFD}$ and the temperature dependence of the residual is cutting 
out the ecliptic plane, restricting to $|\beta|>20^{\circ}$ . In this case, we 
completely eliminated the bending behavior of the residual versus 
$E(B-V)_{SFD}$, and significantly reduced the $T_2$ dependence (see Figure
\ref{fig:resid_ecl}), to a peak-to-peak amplitude of only $\sim$10 mmag. We
still included the single-MBB plots (right column), to show that 
the bend versus $E(B-V)_{SFD}$ is eliminated by the $|\beta|$ cut, even
for the single-MBB model. However, the single-MBB residuals still differ
systematically from zero for $T$$\lesssim$$19$ K. Perhaps these improvements in
the two-component reddening residuals after restricting to high ecliptic 
latitude should come as no surprise, given that the ecliptic plane is the most 
obvious systematic problem with our temperature map upon inspecting the 
full-sky results shown in Figure \ref{fig:results}.

@@

After cutting the ecliptic plane, we found that only small zero level
perturbations were required to fully flatten the temperature residuals,
while still maintaining flat residuals versus $E(B-V)_{SFD}$. The optimal
offsets we found were $\pm$0.08 MJy/sr to \verb|i100| and 857 GHz respectively
(see Figure \ref{fig:resid_offs}). These offsets are well within reason, 
given the nominal zero level uncertainties quoted in Table QQ.

\begin{figure}
\begin{center}
\epsfig{file=resid_offs.eps, width=3.3in}
\caption{\label{fig:resid_offs} $E(B-V)_{2comp}$ residuals as a function of
SFD $E(B-V)$, including a cut on ecliptic latitude, $|\beta|>20^{\circ}$, 
and zero level perturbations of $\pm$0.08 MJy/sr to i100 and 
857 GHz respectively. The grayscale represents the conditional probability 
within each bin in SFD $E(B-V)$. The central black line shows the moving 
median. The upper and lower black lines represent the moving 75th and 25th 
percentiles respectively.}
\end{center}
\end{figure}
